An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2016-10-04 nips_2016.tex
updates

\subsection{Bounds on the Stationary Distribution}
Bounds on the error of an M-H test imply bounds on the stationary
distributed of the Markov chain under appropriate conditions. Such
bounds were derived in both ~\cite{cutting_mh_2014}
and~\cite{icml2014c1_bardenet14}. We include the result from
~\cite{cutting_mh_2014} (Theorem 1) here: Let $d_v(P,Q)$ denote the total
variation distance between two distributions $P$ and $Q$.  Let
$\mathcal{T}_0$ denote the transition kernel of the exact Markov
chain, and $\mathcal{S}_0$ denote the exact posterior distribution.
\begin{lemma}
 If $\mathcal{T}_0$ satisfies the contraction
  condition $d_v(P\mathcal{T}_0,\mathcal{S}_0) < \eta
  d_v(P,\mathcal{S}_0)$ for some constant $\eta\in [0,1)$ and all
    probability distributions $P$, then
    \begin{equation}
      d_v(S_0, S_{\epsilon}) \leq\frac{\epsilon}{1-\eta}
    \end{equation}
\end{lemma}

>>>>

\subsection{Bounds on the Stationary Distribution}
Bounds on the error of an M-H test imply bounds on the stationary
distributed of the Markov chain under appropriate conditions. Such
bounds were derived in both ~\cite{cutting_mh_2014}
and~\cite{icml2014c1_bardenet14}. We include the result from
~\cite{cutting_mh_2014} (Theorem 1) here: Let $d_v(P,Q)$ denote the total
variation distance between two distributions $P$ and $Q$.  Let
$\mathcal{T}_0$ denote the transition kernel of the exact Markov
chain, $\mathcal{S}_0$ denote the exact posterior distribution,
and  $\mathcal{S}_{\epsilon}$ denote the stationary distribution
of the approximate transition kernel. 
\begin{lemma}
 If $\mathcal{T}_0$ satisfies the contraction
  condition $d_v(P\mathcal{T}_0,\mathcal{S}_0) < \eta
  d_v(P,\mathcal{S}_0)$ for some constant $\eta\in [0,1)$ and all
    probability distributions $P$, then
    \begin{equation}
      d_v(S_0, S_{\epsilon}) \leq\frac{\epsilon}{1-\eta}
    \end{equation}
where $\epsilon$ is the bound on the error in the acceptance test. 
\end{lemma}
